Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-27 main_paper.tex
Rewrite Theorem 1 proof slightly
Hopefully this rewrite makes the proof a little easier to read. No real
changes have been made to the arguments, though.

\newpage\appendix
\section{Mathematical Appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau - \Delta^* - \tau = (\hat\tau - \E \hat \tau) +
  (\E \hat \tau - \tau) - (\E^* \hat \tau^* - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{equation*}
  \label{eq:6}
  \E^* \hat\mu_{\pm}^*(h_n) - \mu_{\pm}^{*} =
  h_n^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h_n)/2,
\end{equation*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align*}
  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
  &= \hat\tau - \E\hat\tau
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau - \E\hat\tau
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
\end{align*}
The second equality holds because
$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
follows from normality of $\hat\tau - \E\hat\tau$ and
$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
similar arguments to CCT's Lemma SA4.D.\qed

>>>>

\newpage\appendix
\section{Mathematical Appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \label{eq:6}
  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
  \label{eq:7}
    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
  \label{eq:8}
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
  &= \hat\tau_h - \E\hat\tau_h
   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
  \label{eq:9}
  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed
